\bf A simple and efficient algorithm for computing approximate Nash equilibria in two-person zero-sum games with imcomplete information\smallskip\hrule\hrule

### 2015-06-07 nips2015.tex
more theory

\title{\bf A simple algorithm for computing approximate Nash equilibria in
  two-person zero-sum games with imcomplete information}
\author{Elvis DOHMATOB\\\email{elvis.dohmatob@inria.fr}}
\institute{
Parietal team, Inria Saclay Ile-de-France, Saclay, France
}

@@

\begin{abstract}
We present a simple primal-dual algorithm for computing approximate
Nash equilibria in two-person zero-sum sequential games with
imcomplete information and perfect recall (like Texas Hold'em
Poker). Our algorithm only performs basic iterations (i.e iterations
involving no calls to external first-order oracles, etc.) and is
applicable to a broad class of two-person zero-sum games including
simultaneous games and sequential games with imcomplete information
and perfect recall. The applicability to the latter kind of games is
thanks to the sequence-form representation
\cite{koller1992complexity}. As an application, we apply our algorithm
to solve Kuhn 3-card Poker.
\end{abstract}

\textbf{keywords}: sequential game; imcomplete information; perfect
recall; sequence-form; Nash equilibrium; primal-dual algoithm;
split-feasibility problem; convex-optimization

\section{Introduction}
\label{sec:intro}
A game-theoretic approach to playing games strategically optimally
consists in computing Nash-equilibria (infact, approximations thereof)
offline, and playing one's part of the equilibrium online. This
technique is the driving-force behind solution concepts like CFR
(\textbf{TODO: add Z.'s ref first!!!}) \cite{lanctot2009monte},
$\text{CFR}^{+}$ \textbf{TODO: add ref!!!}, and other variants, which
have recently had profound success in Poker. However, solving games
for equilibria remains a mathematical and computational challenge,
especially in sequential games with imperfect information. This paper
proposes a simple and fast algorithm for solving for such equilibria
approximately, in a sense which will be made clear shortly.

\paragraph{\textbf{Notation and terminology.}}
Let $m$ and $n$ be positive integers.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  The
components of a vector $z \in \mathbb{R}^n$ will be denoted $z_0$,
$z_1$, ..., $z_{n-1}$ (indexing begins from $0$, and not $1$). The
notation ``$z \ge 0$'' means that all the components of $z$ are
nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in
\mathbb{R}^n$, %% $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined
%% by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise
maximum of $z$ with $0$.
%% For example, $((-2, \pi))_+ = (max(-2, 0),
%% max(\pi, 0)) = (0, \pi)$.
The operator $(.)_+$ is the well-known
(multi-dimensional) \textit{ramp} function.
$\mathbb{R}^{m \times n}$ denotes the space of all $m$-by-$n$ real
matrices, $I_m$ denotes the $m$-by-$m$ identity matrix, and $0_{m,n}$
denotes the $m$-by-$n$ matrix of zeros.

Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
  norm}, denoted $\|A\|$, is
 defined to be the largest \textit{singular value} of $A$, i.e the
 largest \textit{eigen-value} of $A^TA$ (or equivalently, of $AA^T$).

Given a subset $C$ of $\mathbb{R}^n$,
$i_C$ denotes its \textit{indicator function} defined by $i_C(x) = 0$
if $ x \in C$; $i_c(x) = \infty$ otherwise.
Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a convex
  function.
The \textit{effective domain} of $f$, denoted $\dom(f)$ is defined as
$\dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}$. If $\dom(f) \ne
\emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
Given $\tau > 0$, the \textit{proximal operator}
of $f$ at rank $\tau$, denoted $\prox_{\tau f}$, is the
function which maps a point $x \in \mathbb{R}^n$ to the (necessarily
unique) minimizer of the $1$-strongly convex function $\mathbb{R}^n
\rightarrow (-\infty,+\infty]$, $z\mapsto \frac{1}{2}\|z - x\|^2 +
  \tau f(z)$.

The interested reader should refer to
\cite{rockafellar1997convex,combettes2011proximal} for a more
elaborate exposition of convex-analytical concepts and their use in
optimization.

@@

\begin{equation}
  0 \le \mathcal{G}(y^*, p^*, x^*, q^*) \le \epsilon
\label{eq:approx_pb}
\end{equation}
\end{definition}

\begin{definition}[\textbf{Nash $(\rho,\epsilon)$-equilibria}]
Given $\rho > 0$ and $\epsilon > 0$, a Nash $(\rho,\epsilon$)-equilibrium is
a pair $(x^*, y^*)$ of realization plans such that there exists dual
vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} such that ...
\end{definition}

\paragraph{\textbf{Our contribution.}}
We develop a $\mathcal{O}(1/\text{min}(\rho,\epsilon))$ primal-dual
algorithm for computing Nash $(\rho, \epsilon$)-equilibria for
sequential two-person zero-sum games with imcomplete information and
perfect recall.

@@

Finally, define the functions $\hat{\Psi}_1$, $\hat{\Psi}_2:
\mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1}
\times \mathbb{R}^{l_2} \rightarrow (-\infty, +\infty]$ by
\begin{eqnarray}
  \left.
  \begin{aligned}
    \hat{\Psi}_1(y, p, x, q) &:=
    \Psi_1(y, p, x, q)+ g_1(y, p) \text{ if }y \ge 0, \hat{\Psi}_1(y,
    p, x, q) := \infty \text{ else}\\
    \hat{\Psi}_2(y, p, x, q) &:= \Psi_2(y, p, x, q)+ g_2(y, p) \text{ if
    }x \ge 0, \hat{\Psi}_2(y,p, x, q) := \infty \text{ else}.
  \end{aligned}
  \right\}
\end{eqnarray}

@@

where $-\infty \le \phi_2(y, p) := \underset{x',q'}{\text{min}}\text{
}\hat{\Psi}_2(y, p, x', q') < +\infty$.
Similarly, the unconstrained objective, say
$b(x, q)$, in the dual LCP \eqref{eq:dual_pb} writes
\begin{eqnarray*}
  \begin{aligned}
 b(x, q) &= 
 -i_{\mathbb{R}^{n_1}_+}(x) - i_{\mathbb{R}^{n_2}_+}(A^Tx+E_2^Tq) -
 i_{\{0\}}(e_1 - E_1x)\\
    &= -g_2(x, q) + \underset{y' \geq
   0}{\text{min}}\text{ }y'^T(A^Tx + E_2^Tq) +
 \underset{p'}{\text{min}}\text{ }p'^T(e_1-E_1x)\\
    &= -g_2(x, q)
 +\underset{y',p'}{\text{max}}\text{ }\Psi_1(y', p', x, q) +
 g_1(y', p') = -g_2(x, q) + \phi_1(x, q),
   \end{aligned}
\end{eqnarray*}
where $-\infty \le \phi_1(x, q) :=
\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p', x, q) < +\infty$.
Thus, one can compute the primal-dual gap between primal LCP
\eqref{eq:primal_pb} and dual LCP \eqref{eq:dual_pb} at $(y, p, x, q)$ as
\begin{eqnarray*}
  \begin{split}
  a(y, p) - b(x, q) &= g_1(y, p) - \phi_2(y, p) + g_2(x, q) - \phi_1(x,
  q) \\
  &= \Psi_1(y, p, x, q) +  g_1(y, p) - \phi_2(y, p) + \Psi_2(y, p, x,
  q) + g_2(x, q) - \phi_1(x, q)\\
  &= \hat{\Psi}_1(y, p, x, q) + \hat{\Psi}_2(y, p, x, q) - \phi_1(x,
  q) - \phi_2(y, p)\\
  &= \text{primal-dual gap of GSP}(\Psi_1, \Psi_2,
  g_1, g_2) \text{ at }(y, p, x, q),
  \end{split}
\end{eqnarray*}
where the second equality follows from the fact that $\Psi_1 + \Psi_2
:= 0$.

@@

\section{The algorithm}
\label{sec:algo}
\textbf{XXX TODO: Define the ergodic variables $\tilde{v}^a$ and
  $\tilde{\epsilon}^a$, ...}

Consider the following algorithm for solving the GSP \eqref{eq:unconstrained_pb}
\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\Require $\rho >0$, $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$.
\Ensure A Nash $(\rho, \epsilon)$-equilibrium
$(\tilde{y},\tilde{p},\tilde{x},\tilde{q}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$,
%% $y^{(0)} \leftarrow 0_{n_2}$,
%% $p^{(0)} \leftarrow 0_{l_1}$, $x^{(0)} \leftarrow 0_{n_1}$, $q^{(0)}
%% \leftarrow 0_{l_2}$,
$k \leftarrow 0$
\While{$\|\tilde{\epsilon}^{a}_k\| \ge \rho$ or $\|\tilde{v}^{a}_k\| \ge \epsilon$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$
\State  \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$
\State  \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} +
\lambda(E_2y^{(k+1)}-e_2)$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda
(A^T(x^{(k+1)}-x^{(k)}) + E_2^T(q^{(k+1)}-q^{(k)}))$
\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1(x^{(k+1)}-x^{(k)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

@@

\begin{proof}
Note that the quadruplet $(\Psi_1, \Psi_2, g_1, g_2)$ clearly satisfies
assumptions B.1, B.2, B.3, B.5, and B.6 of \cite{he2013accelerating}
with $L_{xx} = L_{yy} = 0$ and $L_{xy} = L_{yx} = \|K\|$. Now,
either of $g_1$ and $g_2$ is a separable sum of
the indicator function of a convex set, whose prox is simply the
euclidean projection onto the set,  and a linear transformation $z
\mapsto a^Tz$ whose prox is simply $z \mapsto z - \tau a$. Thus,  one
computes their respective proximal operators $\prox_{\tau g_1} :
\mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow \mathbb{R}^{n_2}
\times \mathbb{R}^{l_1}$, $\prox_{\sigma g_2}: \mathbb{R}^{n_1} \times
\mathbb{R}^{l_2} \rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}$
$\prox_{\lambda g_1}(y, p) = ((y)_+, p - \lambda e_1)$ and $\prox_{\lambda
  g_2}(x, q) = ((x)_+, q - \lambda e_2)$. Algorithm \ref{Tab:algo} is
then obtained from \cite[Algorithm
  T-BD]{he2013accelerating}, applied on the GSP \eqref{eq:unconstrained_pb}
 with the choice of parameters: $\sigma = 1 \in (0, 1]$, $\sigma_x =
         \sigma_y = 0 \in [0, \sigma)$,
 $\lambda_{xy} := \frac{\sqrt{(\sigma^2 - \sigma_x^2)(\sigma^2 -
               \sigma_y^2)}}{\sigma L_{xy}} = \sigma / \|K\| =
           1/\|K\|$, and $\lambda = \lambda_{xy} \in (0,
           \lambda_{xy}]$. The convergence result then follows from
         \cite[Theorem 4.2]{he2013accelerating}.
\end{proof}
\subsection{Practical considerations}
\paragraph{\textbf{Efficient computation of $Ay$ and $A^Tx$.}}
In Algorithms \ref{Tab:algo} most of the time is spent
pre-multiplying vectors by $A$ and $A^T$. For \textit{flop}-type Poker
games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em},
$A$ (and thus $A^T$ too)  is very big (up $10^{14}$ rows and columns!)
but has a rich block-diagnoal structure which can be carefully
exploited, as was done in \cite{hoda2010smoothing}.

>>>>

\title{\bf A simple and efficient algorithm for computing approximate
  Nash equilibria in two-person zero-sum games with imcomplete
  information\smallskip\hrule\hrule}
\author{Elvis DOHMATOB\\\email{elvis.dohmatob@inria.fr}}
\institute{
Parietal team, Inria Saclay Ile-de-France, Saclay, France
}

@@

\begin{abstract}
We present a simple primal-dual algorithm for computing approximate
Nash equilibria in two-person zero-sum sequential games with
imcomplete information and perfect recall (like Texas Hold'em
Poker). Our algorithm only performs basic iterations (i.e iterations
involving no calls to external first-order oracles, etc.) and is
applicable to a broad class of two-person zero-sum games including
simultaneous games and sequential games with imcomplete information
and perfect recall. The number of iterations need to produce a Nash
equilibrium with a given precision is inversely proportion to the
precision. The applicability to the latter kind of games is thanks to
the sequence-form representation \cite{koller1992complexity}. As
proof-of-concept, we apply our algorithm to solve Kuhn 3-card Poker.
\end{abstract}

\textbf{keywords}: sequential game; imcomplete information; perfect
recall; sequence-form; approximate Nash equilibrium; primal-dual
algoithm; convex-optimization

\section{Introduction}
\label{sec:intro}
\paragraph{\textbf{Context.}}
A game-theoretic approach to playing games strategically optimally
consists in computing Nash-equilibria (infact, approximations thereof)
offline, and playing one's part of the equilibrium online. This
technique is the driving-force behind solution concepts like CFR
(\textbf{TODO: add Z.'s ref first!!!}) \cite{lanctot2009monte},
$\text{CFR}^{+}$ \textbf{TODO: add ref!!!}, and other variants, which
have recently had profound success in Poker. However, solving games
for equilibria remains a mathematical and computational challenge,
especially in sequential games with imperfect information. This paper
proposes a simple and fast algorithm for solving for such equilibria
approximately, in a sense which will be made clear shortly.

\paragraph{\textbf{Notation and terminology.}}
Let $m$ and $n$ be positive integers.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  The
components of a vector $z \in \mathbb{R}^n$ will be denoted $z_0$,
$z_1$, ..., $z_{n-1}$ (indexing begins from $0$, and not $1$). The
notation ``$z \ge 0$'' means that all the components of $z$ are
nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in
\mathbb{R}^n$, %% $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined
%% by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise
maximum of $z$ with $0$.
%% For example, $((-2, \pi))_+ = (max(-2, 0),
%% max(\pi, 0)) = (0, \pi)$.
The operator $(.)_+$ is the well-known
(multi-dimensional) \textit{ramp} function.
$\mathbb{R}^{m \times n}$ denotes the space of all $m$-by-$n$ real
matrices, $I_m$ denotes the $m$-by-$m$ identity matrix, and $0_{m,n}$
denotes the $m$-by-$n$ matrix of zeros.
Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
  norm}, denoted $\|A\|$, is
 defined to be the largest \textit{singular value} of $A$, i.e the
 largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).

Given a subset $C$ of $\mathbb{R}^n$,
$i_C$ denotes its \textit{indicator function} defined by
\begin{eqnarray}
  i_C(x) = 0, \text{ if } x \in C;\hspace{.3em} i_c(x) = \infty\text{
    otherwise.}
\end{eqnarray}

Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a convex
  function.
The \textit{effective domain} of $f$, denoted $\dom(f)$ is defined as
\begin{eqnarray}
  \dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
\end{eqnarray}
 If $\dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
Given $\tau > 0$, the function
\begin{eqnarray}
  \prox_{\tau f}: \mathbb{R}^n \rightarrow \mathbb{R}^n,\hspace{.5em}x
  \mapsto \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
  - x\|^2 + \tau f(z),
\end{eqnarray}

is called the \textit{proximal operator} of $f$ at rank $\tau$.
The interested reader should refer to
\cite{rockafellar1997convex,combettes2011proximal} for a more
elaborate exposition of convex-analytical concepts and their use in
optimization.

@@

\begin{equation}
  0 \le \mathcal{G}(y^*, p^*, x^*, q^*) \le \epsilon
\label{eq:approx_pb}
\end{equation}
\label{thm:approx_nash}
\end{definition}

\paragraph{\textbf{Our contribution.}}
We develop a $\mathcal{O}(1/\text{min}(\rho,\epsilon))$ primal-dual
algorithm for computing Nash $(\rho, \epsilon$)-equilibria (in a sense
to be made clear later) for
sequential two-person zero-sum games with imcomplete information and
perfect recall.

@@

Finally, define the functions $\hat{\Psi}_1$, $\hat{\Psi}_2:
\mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1}
\times \mathbb{R}^{l_2} \rightarrow (-\infty, +\infty]$ by
\begin{eqnarray}
  \left.
  \begin{aligned}
    \hat{\Psi}_1(y, p, x, q) &:=
    \Psi_1(y, p, x, q)+ g_1(y, p) \text{ if }y \ge 0, \hat{\Psi}_1(y,
    p, x, q) := \infty \text{ else}\\
    \hat{\Psi}_2(y, p, x, q) &:= \Psi_2(y, p, x, q)+ g_2(x, q) \text{ if
    }x \ge 0, \hat{\Psi}_2(y,p, x, q) := \infty \text{ else}.
  \end{aligned}
  \right\}
\end{eqnarray}

@@

where $-\infty \le \phi_2(y, p) := \underset{x',q'}{\text{min}}\text{
}\hat{\Psi}_2(y, p, x', q') < +\infty$.
Similarly, the unconstrained objective, say
$b(x, q)$, in the dual LCP \eqref{eq:dual_pb} writes
\begin{eqnarray*}
  \begin{aligned}
 b(x, q) &= 
 -i_{\mathbb{R}^{n_1}_+}(x) - i_{\mathbb{R}^{n_2}_+}(A^Tx+E_2^Tq) -
 i_{\{0\}}(e_1 - E_1x)\\
    &= -g_2(x, q) + \underset{y' \geq
   0}{\text{min}}\text{ }y'^T(A^Tx + E_2^Tq) +
 \underset{p'}{\text{min}}\text{ }p'^T(e_1-E_1x)\\
    &= -g_2(x, q)
 +\underset{y',p'}{\text{max}}\text{ }\Psi_1(y', p', x, q) +
 g_1(y', p') = -g_2(x, q) + \phi_1(x, q),
   \end{aligned}
\end{eqnarray*}
where $-\infty \le \phi_1(x, q) :=
\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p', x, q) < +\infty$.
Thus, one can compute the primal-dual gap between primal LCP
\eqref{eq:primal_pb} and dual LCP \eqref{eq:dual_pb} at $(y, p, x, q)$ as
\begin{eqnarray*}
  \begin{split}
  a(y, p) - b(x, q) &= g_1(y, p) - \phi_2(y, p) + g_2(x, q) - \phi_1(x,
  q) \\
  &= \Psi_1(y, p, x, q) +  g_1(y, p) - \phi_2(y, p) + \Psi_2(y, p, x,
  q) + g_2(x, q) - \phi_1(x, q)\\
  &= \hat{\Psi}_1(y, p, x, q) + \hat{\Psi}_2(y, p, x, q) - \phi_1(x,
  q) - \phi_2(y, p)\\
  &= \text{primal-dual gap of GSP}(\Psi_1, \Psi_2,
  g_1, g_2) \text{ at }(y, p, x, q),
  \end{split}
\end{eqnarray*}
where the second equality follows from the fact that $\Psi_1 + \Psi_2
:= 0$.
\qed

@@

\section{The proposed algorithm}
\label{sec:algo}
In this section we derive the algorithm which is the main object of
this manuscript.

\subsection{Relaxing the conditions for equilibrium}
Let us first introduce the notion of $\epsilon$-subgradients. The idea
is to replace the usual optimality characterization ``$x$ optimal iff
$0 \in \partial f(x)$'' with ``$x$ approx optimal iff $0 \in
\partial_\epsilon f(x)$''. In fact, letting $\epsilon \rightarrow 0^+$,
$\partial f(x) = \partial_{0^+}f(x)$ will coincide with
subgradient of $f$ at $x$, namely $\{h\in X | f(z) \ge f(x) + \langle
h, z - x\rangle \forall z \in X\}$.

\begin{definition}[$\epsilon$-subgradient]
Given a scalar $\epsilon > 0$ and a function $f:X \subseteq \mathbb{R}^n
\rightarrow [-\infty,+\infty]$, the $\epsilon$-subgradient of $f$ the
set-valued function
\begin{eqnarray}
\partial_\epsilon f: X \mapsto 2^X, \hspace{.5em} x \mapsto \{h\in X |
f(z) + \epsilon \ge f(x) + \langle h, z - x\rangle \forall z \in X\}.
\end{eqnarray}
\end{definition}

%% Since won't typically be able to compute a feasible point in $Q_1 \in
%% Q_2$ (due to the equality constraints $E_kz = e_k$), we will consider
%% an approximate equilibrium concept which takes in to account the
%% distance from the set of equilibria. Viz,

\begin{definition}[\textbf{Nash $(\rho,\epsilon)$-equilibria}]
Given $\rho > 0$ and $\epsilon > 0$, a Nash
$(\rho,\epsilon$)-equilibrium is a pair $(x^*, y^*)$ of realization
plans such that there exists dual vectors $p^*$ and $q^*$ and a
pertubation vector $v^*$ for which
\begin{eqnarray}
\|v^*\| \le \rho \text{ and}\hspace{.5em} v^* \in
\partial_\epsilon[\hat{\Psi}_1(., ., x^*, q^*) +
  \hat{\Psi}_2(y^*, p^*, , .)](y^*,p^*,x^*,q^*).
\end{eqnarray}
\end{definition}

The above definition is a generalization of the notion of Nash
equilibria in the sense that
\begin{itemize}
\item Exact Nash equilibria correspond to Nash $(0^+,0^+)$-equilibria.
\item Nash $\epsilon$-equilibria (in the sense of Definition
  \ref{thm:approx_nash}) correspond to Nash $(0^+,\epsilon)$-equilibria.
\end{itemize}

%\paragraph{\textbf{Plan of attack.}}
\textbf{XXX TODO: Define the ergodic variables $\tilde{v}^a$ and
  $\tilde{\epsilon}^a$, ...}

\subsection{The algorithm proper and its convergence rate}
Consider the following algorithm for solving the GSP
\eqref{eq:unconstrained_pb}
\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\Require $\rho >0$, $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$.
\Ensure A Nash $(\rho, \epsilon)$-equilibrium
$(\tilde{y},\tilde{p},\tilde{x},\tilde{q}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$,
%% $y^{(0)} \leftarrow 0_{n_2}$,
%% $p^{(0)} \leftarrow 0_{l_1}$, $x^{(0)} \leftarrow 0_{n_1}$, $q^{(0)}
%% \leftarrow 0_{l_2}$,
$k \leftarrow 0$
\While{$\|\tilde{\epsilon}^{a}_k\| \ge \rho$ or $\|\tilde{v}^{a}_k\| \ge \epsilon$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$
\State  \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$
\State  \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} +
\lambda(E_2y^{(k+1)}-e_2)$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda
(A^T(x^{(k+1)}-x^{(k)}) + E_2^T(q^{(k+1)}-q^{(k)}))$
\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1(x^{(k+1)}-x^{(k)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

@@

\begin{proof}
Note that the quadruplet $(\Psi_1, \Psi_2, g_1, g_2)$ clearly satisfies
assumptions B.1, B.2, B.3, B.5, and B.6 of \cite{he2013accelerating}
with $L_{xx} = L_{yy} = 0$ and $L_{xy} = L_{yx} = \|K\|$. Now,
one easily computes the proximal operators $g_1$ and $g_2$ as
\begin{eqnarray*}
  \prox_{\lambda g_1}(y, p) \equiv ((y)_+, p - \lambda
  e_1),\hspace{.5em} \prox_{\lambda g_2}(x, q) \equiv ((x)_+, q -
  \lambda e_2).
  \end{eqnarray*}

Algorithm \ref{Tab:algo} is then obtained from \cite[Algorithm
  T-BD]{he2013accelerating}, applied on the GSP
\eqref{eq:unconstrained_pb} with the choice of parameters: $\sigma = 1
\in (0, 1]$, $\sigma_x = \sigma_y = 0 \in [0, \sigma)$,
    $\lambda_{xy} := \frac{\sqrt{(\sigma^2 - \sigma_x^2)(\sigma^2 -
        \sigma_y^2)}}{\sigma L_{xy}} = \sigma / \|K\| =
    1/\|K\|$, and $\lambda = \lambda_{xy} \in (0,
    \lambda_{xy}]$. The convergence result follows immediately from
  \cite[Theorem 4.2]{he2013accelerating}.
  \qed
\end{proof}

\subsection{Practical considerations}
\paragraph{\textbf{Efficient computation of $Ay$ and $A^Tx$.}}
In Algorithms \ref{Tab:algo} most of the time is spent
pre-multiplying vectors by $A$ and $A^T$. For \textit{flop}-type Poker
games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em},
$A$ (and thus $A^T$ too)  is very big (up $10^{14}$ rows and columns!)
but has a rich block-diagnoal structure which can be carefully
exploited, as was done in \cite{hoda2010smoothing}.
